---
title: "R Notebook"
output: html_notebook
---

Part 1: Alignment of fingerprint-derived clusters with structural and biosynthetic classes

```{r}
#Load libraries
library(aricode)
library(mclust)
library(dplyr)
library(tidyr)
library(ggplot2)
library(pheatmap)
library(ggplot2)
library(dplyr)
```


```{r}
#NMI/ARI calculation at Structural class level
df<-read.csv("Cluster_results_new.csv", header = T, check.names = F)
as.data.frame(df)->df
ground_truth <- df$Structural_class
cluster_cols <- colnames(df)[4:ncol(df)]
results_Str <- data.frame(
  Method = character(),
  NMI = numeric(),
  ARI = numeric(),
  stringsAsFactors = FALSE
)
for (col in cluster_cols) {
  clusters <- df[[col]]
  valid_idx <- !is.na(clusters) & !is.na(ground_truth)
  clusters_clean <- as.vector(clusters[valid_idx])
  truth_clean <- as.vector(ground_truth[valid_idx])
  nmi_val <- NMI(clusters_clean, truth_clean)
  ari_val <- adjustedRandIndex(clusters_clean, truth_clean)
  results_Str <- rbind(results_Str, data.frame(
    Method = col,
    NMI = nmi_val,
    ARI = ari_val,
    stringsAsFactors = FALSE
  ))
}

results_Str

#NMI/ARI calculation at Biosynthetic class level
ground_truth <- df$Biosynthetic_class
cluster_cols <- colnames(df)[4:ncol(df)]
results_bio <- data.frame(
  Method = character(),
  NMI = numeric(),
  ARI = numeric(),
  stringsAsFactors = FALSE
)
for (col in cluster_cols) {
  clusters <- df[[col]]
  valid_idx <- !is.na(clusters) & !is.na(ground_truth)
  clusters_clean <- as.vector(clusters[valid_idx])
  truth_clean <- as.vector(ground_truth[valid_idx])
  nmi_val <- NMI(clusters_clean, truth_clean)
  ari_val <- adjustedRandIndex(clusters_clean, truth_clean)
  results_bio <- rbind(results_bio, data.frame(
    Method = col,
    NMI = nmi_val,
    ARI = ari_val,
    stringsAsFactors = FALSE
  ))
}

results_bio

#Plotting NMI versus ARI to check for the best or optimal clusters
#For Structural classes:
Method<-results_Str$Method
Str <- results_Str %>% 
  separate(Method,            
           into  = c("Type", "Cluster", "Method"),
           sep   = "_",      
           remove = TRUE) %>% 
  mutate(
    Cluster = as.integer(Cluster),            
  )

#Plot in graph
Str <- Str %>%
  mutate(Cluster = as.integer(Cluster))     
k_breaks <- sort(unique(Str$Cluster))
p_nmi <- ggplot(Str,
                aes(x = Cluster,
                    y = NMI,
                    colour = Method,
                    group  = Method)) +
  geom_line(size = 1) +
  geom_point(size = 3) +
  facet_wrap(~ Type, nrow = 1) +
  scale_x_continuous(breaks = k_breaks) + 
  labs(x = "Number of clusters (k)",
       y = "Normalized Mutual Information (NMI)",
       colour = "Clustering method") +
  theme_bw(base_size = 12) +
  theme(panel.spacing  = unit(1, "lines"),
        legend.position = "bottom")

p_nmi

#Plot ARI
p_ari <- ggplot(Str,
                aes(x = Cluster,
                    y = ARI,
                    colour = Method,
                    group  = Method)) +
  geom_line(size = 1) +
  geom_point(size = 3) +
  facet_wrap(~ Type, nrow = 1) +
  scale_x_continuous(breaks = k_breaks) +     
  labs(x = "Number of clusters (k)",
       y = "Adjusted rand index (ARI)",
       colour = "Clustering method") +
  theme_bw(base_size = 12) +
  theme(panel.spacing  = unit(1, "lines"),
        legend.position = "bottom")

p_ari

#Plots for Biosynthetic classes
#NMI plots
Method<-results_bio$Method
Bio <- results_bio %>% 
  separate(Method,            
           into  = c("Type", "Cluster", "Method"),
           sep   = "_",      
           remove = TRUE) %>% 
  mutate(
    Cluster = as.integer(Cluster),              
  )

#NMI:Biosynthetic: All
Bio <- Bio %>%
  mutate(Cluster = as.integer(Cluster))        
k_breaks <- sort(unique(Bio$Cluster))
#plot
p_nmi <- ggplot(Bio,
                aes(x = Cluster,
                    y = NMI,
                    colour = Method,
                    group  = Method)) +
  geom_line(size = 1) +
  geom_point(size = 3) +
  facet_wrap(~ Type, nrow = 1) +
  scale_x_continuous(breaks = k_breaks) +     # << makes every k tick appear
  labs(x = "Number of clusters (k)",
       y = "Normalized Mutual Information (NMI)",
       colour = "Clustering method") +
  theme_bw(base_size = 12) +
  theme(panel.spacing  = unit(1, "lines"),
        legend.position = "bottom")

p_nmi

#ARI:Biosynthetic: All
p_ari <- ggplot(Bio,
                aes(x = Cluster,
                    y = ARI,
                    colour = Method,
                    group  = Method)) +
  geom_line(size = 1) +
  geom_point(size = 3) +
  facet_wrap(~ Type, nrow = 1) +
  scale_x_continuous(breaks = k_breaks) +     
  labs(x = "Number of clusters (k)",
       y = "Adjusted Rand Index (ARI)",
       colour = "Clustering method") +
  theme_bw(base_size = 12) +
  theme(panel.spacing  = unit(1, "lines"),
        legend.position = "bottom")
p_ari

#Contingency heatmaps for all combinations: k-means clustering for structural classes across fingerprint types
#Reading the dataframe
df<-read.csv("Clusters_Kmeans_FPs.csv", header = T, check.names = F, stringsAsFactors=FALSE)
generate_cluster_heatmap <- function(df, class_col = "Structural_class") {
  df_long <- df %>%
    pivot_longer(
      cols = starts_with("EXT"):last_col(),  
      names_to = "fingerprint_k",
      values_to = "cluster"
    ) %>%
    mutate(
      fingerprint = str_extract(fingerprint_k, "^[a-zA-Z]+"),
      k = str_extract(fingerprint_k, "k\\d+") %>% str_remove("k") %>% as.integer()
    )
  heatmap_data <- df_long %>%
    group_by(!!sym(class_col), fingerprint, k, cluster) %>%
    summarise(n = n(), .groups = "drop") %>%
    group_by(!!sym(class_col), fingerprint, k) %>%
    mutate(percentage = 100 * n / sum(n)) %>%
    ungroup()
  heatmap_data <- heatmap_data %>%
    mutate(
      cluster = factor(cluster),
      class = as.factor(!!sym(class_col)),
      label = sprintf("%.1f", percentage)  
    )

#Plot
  ggplot(heatmap_data, aes(x = cluster, y = class, fill = percentage)) +
    geom_tile(color = "white") +
    geom_text(aes(label = label), size = 3) +
    scale_fill_gradient(low = "white", high = "steelblue") +
    facet_grid(k ~ fingerprint, scales = "fixed", space = "free_x") +
    labs(x = "Cluster", y = class_col, fill = "% in cluster") +
    theme_minimal(base_size = 12) +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),
      strip.text = element_text(face = "bold")
    )
}

# For K-means clustering vs structural class
generate_cluster_heatmap(df, class_col = "Structural_class")

#Contingency heatmaps for all combinations: k-means clustering for biosynthetic classes across fingerprint types
generate_cluster_heatmap <- function(df, class_col = "Biosynthetic_class", class_order = NULL) {
  df_long <- df %>%
    pivot_longer(
      cols = starts_with("EXT"):last_col(),
      names_to = "fingerprint_k",
      values_to = "cluster"
    ) %>%
    mutate(
      fingerprint = str_extract(fingerprint_k, "^[a-zA-Z]+"),
      k = str_extract(fingerprint_k, "k\\d+") %>% str_remove("k") %>% as.integer()
    )

  heatmap_data <- df_long %>%
    group_by(!!sym(class_col), fingerprint, k, cluster) %>%
    summarise(n = n(), .groups = "drop") %>%
    group_by(!!sym(class_col), fingerprint, k) %>%
    mutate(percentage = 100 * n / sum(n)) %>%
    ungroup()

  heatmap_data <- heatmap_data %>%
    mutate(
      cluster = factor(cluster),
      class = !!sym(class_col),
      class = if (!is.null(class_order)) factor(class, levels = class_order) else factor(class),
      label = sprintf("%.1f", percentage)
    )

  ggplot(heatmap_data, aes(x = cluster, y = class, fill = percentage)) +
    geom_tile(color = "white") +
    geom_text(aes(label = label), size = 1.5) +
    scale_fill_gradient(low = "white", high = "steelblue") +
    facet_grid(k ~ fingerprint, scales = "free_x", space = "free_x") +
    labs(x = "Cluster", y = class_col, fill = "% in cluster") +
    theme_minimal(base_size = 6) +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),
      strip.text = element_text(face = "bold")
    )
}

biosynthetic_order <-c("Shikimate_derived_Aromatics", "Terpenoids", "FADs", "Others")


generate_cluster_heatmap(
  df = df,
  class_col = "Biosynthetic_class",
  class_order = biosynthetic_order
)

#Contingency heatmaps for all combinations: Agglomerative clustering for structural classes across fingerprint types
df<-read.csv("Clusters_Agglo_FPs.csv", header = T, check.names = F, stringsAsFactors=FALSE)

generate_cluster_heatmap <- function(df, class_col = "Structural_class", class_order = NULL) {
  df_long <- df %>%
    pivot_longer(
      cols = starts_with("EXT"):last_col(),
      names_to = "fingerprint_k",
      values_to = "cluster"
    ) %>%
    mutate(
      fingerprint = str_extract(fingerprint_k, "^[a-zA-Z]+"),
      k = str_extract(fingerprint_k, "k\\d+") %>% str_remove("k") %>% as.integer()
    )

  heatmap_data <- df_long %>%
    group_by(!!sym(class_col), fingerprint, k, cluster) %>%
    summarise(n = n(), .groups = "drop") %>%
    group_by(!!sym(class_col), fingerprint, k) %>%
    mutate(percentage = 100 * n / sum(n)) %>%
    ungroup()

  heatmap_data <- heatmap_data %>%
    mutate(
      cluster = factor(cluster),
      class = !!sym(class_col),
      class = if (!is.null(class_order)) factor(class, levels = class_order) else factor(class),
      label = sprintf("%.1f", percentage)
    )

  ggplot(heatmap_data, aes(x = cluster, y = class, fill = percentage)) +
    geom_tile(color = "white") +
    geom_text(aes(label = label), size = 1.5) +
    scale_fill_gradient(low = "white", high = "steelblue") +
    facet_grid(k ~ fingerprint, scales = "free", space = "free") +
    labs(x = "Cluster", y = class_col, fill = "% in cluster") +
    theme_minimal(base_size = 6) +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),
      strip.text = element_text(face = "bold")
    )
}

structural_order <-c("BP","Aromatic_N/S","NonAromatic_N/S","MT", "ST","Diterpenes","Irregular terpene","Aliphatics and C5 branched","Others")


generate_cluster_heatmap(
  df = df,
  class_col = "Structural_class",
  class_order = structural_order
)

#Contingency heatmaps for all combinations: Agglomerative clustering for biosynthetic classes across fingerprint types
generate_cluster_heatmap <- function(df, class_col = "Biosynthetic_class", class_order = NULL) {
  df_long <- df %>%
    pivot_longer(
      cols = starts_with("EXT"):last_col(),
      names_to = "fingerprint_k",
      values_to = "cluster"
    ) %>%
    mutate(
      fingerprint = str_extract(fingerprint_k, "^[a-zA-Z]+"),
      k = str_extract(fingerprint_k, "k\\d+") %>% str_remove("k") %>% as.integer()
    )

  heatmap_data <- df_long %>%
    group_by(!!sym(class_col), fingerprint, k, cluster) %>%
    summarise(n = n(), .groups = "drop") %>%
    group_by(!!sym(class_col), fingerprint, k) %>%
    mutate(percentage = 100 * n / sum(n)) %>%
    ungroup()
  heatmap_data <- heatmap_data %>%
    mutate(
      cluster = factor(cluster),
      class = !!sym(class_col),
      class = if (!is.null(class_order)) factor(class, levels = class_order) else factor(class),
      label = sprintf("%.1f", percentage)
    )
  ggplot(heatmap_data, aes(x = cluster, y = class, fill = percentage)) +
    geom_tile(color = "white") +
    geom_text(aes(label = label), size = 1.5) +
    scale_fill_gradient(low = "white", high = "steelblue") +
    facet_grid(k ~ fingerprint, scales = "free", space = "free") +
    labs(x = "Cluster", y = class_col, fill = "% in cluster") +
    theme_minimal(base_size = 6) +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),
      strip.text = element_text(face = "bold")
    )
}

biosynthetic_order <-c("Shikimate_derived_Aromatics", "Terpenoids", "FADs", "Others")

generate_cluster_heatmap(
  df = df,
  class_col = "Biosynthetic_class",
  class_order = biosynthetic_order
)
```


Part 2: Plots for taxonomic rank prediction

```{r}
#Load required libraries
library(tidyverse)
library(ggplot2)
library(dplyr)
library(readr)
```


```{r}
#(2a) Recall bar plots
#With fingerprints
#Order-level
#Read in the classification metrics file for order 
df<-read.csv("classification_report_EXT_torder_MLPClassifier.csv", check.names = FALSE)
df<-df[-c(39:41),]
df$Recall_Percent <- df$recall * 100
df <- df %>%
  arrange(support) %>%
  mutate(Orders = factor(Orders, levels = Orders))  

#Plot
p<-ggplot(df, aes(x = Orders, y = Recall_Percent)) +
  
  geom_bar(stat = "identity", fill = NA, color = "black", linewidth = 0.4, width = 0.6) +

  
  geom_text(aes(label = support),
            vjust = -0.5,
            size = 1.5,
            family = "Times") +
  scale_y_continuous(
    limits = c(0, max(df$Recall_Percent) + 10),
    breaks = seq(0, 100, by = 10),
    expand = expansion(mult = c(0, 0.05))
  ) +
  labs(
    x = "Plant Orders",
    y = "Recall (%)",
    title = "Recall by Plant Orders"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 90, hjust = 1, size = 5),
    axis.text.y = element_text(size = 5),
    axis.title.x = element_text(size = 6, face = "bold"),
    axis.title.y = element_text(size = 6, face = "bold"),
    plot.title  = element_text(size = 8, face = "bold"),
    panel.grid  = element_blank(),
    panel.border = element_blank(),
    axis.line = element_line(color = "black", linewidth = 0.5),
    axis.ticks = element_line(color = "black", linewidth = 0.3),
    axis.ticks.length = unit(0.1, "cm")
  )

p

#With fingerprints
#Family-level
#Read the classification metrics for family
df<-read.csv("classification_report_EXT_tfamily_MLPClassifier.csv", check.names = FALSE)
df<-df[-c(71:73),]
df$Recall_Percent <- df$recall * 100
df <- df %>%
  arrange(support) %>%
  mutate(Family = factor(Family, levels = Family)) 

#Plot
p<-ggplot(df, aes(x = Family, y = Recall_Percent)) +
  geom_bar(stat = "identity", fill = NA, color = "black", linewidth = 0.4, width = 0.6) +
  geom_text(aes(label = support),
            vjust = -0.5,
            size = 1.1,
            family = "Times") +
  scale_y_continuous(
    limits = c(0, max(df$Recall_Percent) + 10),
    breaks = seq(0, 100, by = 10),
    expand = expansion(mult = c(0, 0.05))
  ) +

  labs(
    x = "Plant Family",
    y = "Recall (%)",
    title = "Recall by Plant Family"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 90, hjust = 1, size = 5),
    axis.text.y = element_text(size = 5),
    axis.title.x = element_text(size = 6, face = "bold"),
    axis.title.y = element_text(size = 6, face = "bold"),
    plot.title  = element_text(size = 8, face = "bold"),
    panel.grid  = element_blank(),
    panel.border = element_blank(),
    axis.line = element_line(color = "black", linewidth = 0.5),
    axis.ticks = element_line(color = "black", linewidth = 0.3),
    axis.ticks.length = unit(0.1, "cm")
  )

p

#(2b) Confusion matrices for best performing model using fingerprints
#Order-level classification: EXT: MLP after CV
#Read the confusion matrix
cm<-read.csv("confusion_matrix_EXT_torder_MLPClassifier.csv", row.names = 1, check.names = FALSE)
head(cm)
#Re-order according to phylogenetic relationships
new_order <- c("Cycadales","Pinales","Chloranthales","Piperales","Canellales","Laurales",
"Magnoliales","Acorales","Alismatales","Asparagales","Pandanales","Liliales",
"Commelinales","Zingiberales","Arecales","Poales","Proteales","Ranunculales","Ericales",
"Dipsacales","Apiales","Asterales","Lamiales","Solanales","Boraginales","Gentianales",
"Caryophyllales","Santalales","Vitales","Saxifragales","Myrtales","Geraniales","Rosales",
"Fabales","Malpighiales","Sapindales","Malvales","Brassicales")

keep <- new_order[new_order %in% rownames(cm)]
cm_ord <- cm[keep, keep]

#Convert to long format
cm_long <- cm_ord %>%
  as.data.frame() %>%
  rownames_to_column("Actual") %>%
  pivot_longer(-Actual, names_to = "Predicted", values_to = "Freq")


cm_long$Actual    <- factor(cm_long$Actual,    levels = keep)  
cm_long$Predicted <- factor(cm_long$Predicted, levels = keep)       

diag_df <- cm_long %>% filter(Actual == Predicted)

#Plot
p<-ggplot(cm_long, aes(Predicted, fct_rev(Actual), fill = Freq)) +
  geom_tile(color = "grey85", linewidth = 0.3) +
  geom_text(aes(label = ifelse(Freq == 0, "", Freq)), size = 3) +
  geom_tile(
    data = diag_df,
    color = "maroon",       
    linewidth = 0.2,      
    fill = NA           
  ) +
  scale_fill_gradient(low = "white", high = "#2c7fb8") +
  labs(title = "Confusion Matrix of Plant Orders", x = "Predicted Order", y = "Actual Order", fill = "Count") +
  theme_minimal(base_size = 10) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid = element_blank()
  ) +
  coord_equal()
p

#Family-level classification: EXT: MLP after CV
#Read the confusion matrix
cm<-read.csv("confusion_matrix_EXT_tfamily_MLPClassifier.csv", row.names = 1, check.names = FALSE)

#Re-order according to relatedness of families
new_order<-c("Cycadaceae","Zamiaceae","Cupressaceae","Pinaceae","Chloranthaceae","Piperaceae","Winteraceae","Lauraceae","Annonaceae","Eupomatiaceae","Magnoliaceae","Myristicaceae","Acoraceae","Araceae","Amaryllidaceae","Orchidaceae","Cyclanthaceae","Liliaceae","Commelinaceae","Zingiberaceae","Arecaceae","Cyperaceae","Poaceae","Nelumbonaceae","Berberidaceae","Ranunculaceae","Actinidiaceae","Lecythidaceae","Polemoniaceae","Primulaceae","Caprifoliaceae","Apiaceae","Asteraceae","Lamiaceae","Oleaceae","Plantaginaceae","Acanthaceae","Orobanchaceae","Verbenaceae","Solanaceae","Boraginaceae","Apocynaceae","Gentianaceae","Rubiaceae","Cactaceae","Caryophyllaceae","Santalaceae","Vitaceae","Grossulariaceae", "Combretaceae","Lythraceae","Myrtaceae","Geraniaceae","Moraceae","Rosaceae","Fabaceae","Hypericaceae","Rhizophoraceae","Salicaceae","Violaceae","Anacardiaceae","Burseraceae","Meliaceae","Rutaceae","Sapindaceae","Bixaceae","Cistaceae","Malvaceae","Thymelaeaceae","Brassicaceae")

keep <- new_order[new_order %in% rownames(cm)]
cm_ord <- cm[keep, keep]

#Convert to long format
cm_long <- cm_ord %>%
  as.data.frame() %>%
  rownames_to_column("Actual") %>%
  pivot_longer(-Actual, names_to = "Predicted", values_to = "Freq")

cm_long$Actual    <- factor(cm_long$Actual,    levels = keep)  
cm_long$Predicted <- factor(cm_long$Predicted, levels = keep)       

diag_df <- cm_long %>% filter(Actual == Predicted)

#Plot
p<-ggplot(cm_long, aes(Predicted, fct_rev(Actual), fill = Freq)) +
  geom_tile(color = "grey85", linewidth = 0.2) +
  geom_text(aes(label = ifelse(Freq == 0, "", Freq)), size = 2) +
  geom_tile(
    data = diag_df,
    color = "maroon",       
    linewidth = 0.2,       
    fill = NA              
  ) +
  scale_fill_gradient(low = "white", high = "#2c7fb8") +
  labs(title = "Confusion Matrix of Plant families", x = "Predicted Family", y = "Actual Family", fill = "Count") +
  theme_minimal(base_size = 10) +
  coord_equal() 
p

#Genus-level classification: Sub: LR after CV
#Read the confusion matrix
cm<-read.csv("confusion_matrix_Sub_tgenus_LogisticRegression.csv", row.names = 1, check.names = FALSE)

#Edit to required genera
#Re-order according to family
selected_taxa<-c("Achillea","Ageratum","Anaphalis","Arnica","Artemisia","Calendula","Carduus","Centaurea","Centratherum","Chamaemelum","Chrysactinia","CRASSOCEPHALUM","Glebionis","Leontopodium","Matricaria","Mikania","Saussurea","Tagetes","Tanacetum","Hypericum","Caryopteris","Clinopodium","Dracocephalum","Elsholtzia","Lavandula","Marrubium","Melissa","Mentha","Monarda","Nepeta","Ocimum","Origanum","Pogostemon","Salvia","Satureja","Stachys","Thymus","Liriodendron","Magnolia","Ficus","Aerangis","Coryanthes","Cymbidium","Cypripedium","Epidendrum","Mystacidium","Ophrys","Peristeria","Phalaenopsis","Vanda","Zygopetalum","Aframomum","Alpinia","Amomum","Hedychium","Zingiber")

#Subset rows and columns for only these taxa
cm_subset <- cm[selected_taxa, selected_taxa]

keep <- selected_taxa[selected_taxa %in% rownames(cm_subset)]
cm_ord <- cm_subset[keep, keep]

#Convert to long format
taxa_order <- colnames(cm_ord)

cm_long <- cm_ord %>%
  as.data.frame() %>%
  rownames_to_column("Actual") %>%
  pivot_longer(-Actual, names_to = "Predicted", values_to = "Freq") %>%
  mutate(
    Actual = factor(Actual, levels = taxa_order),
    Predicted = factor(Predicted, levels = taxa_order)
  )

diag_df <- cm_long %>% filter(Actual == Predicted)

# Plot
p<-ggplot(cm_long, aes(Predicted, fct_rev(Actual), fill = Freq)) +
  geom_tile(color = "grey85", linewidth = 0.2) +
  geom_text(aes(label = ifelse(Freq == 0, "", Freq)), size = 2) +
  geom_tile(
    data = diag_df,
    color = "maroon",       
    linewidth = 0.2,      
    fill = NA             
  ) +
  scale_fill_gradient(low = "white", high = "#2c7fb8") +
  labs(title = "Confusion Matrix of Plant Genera", x = "Predicted Genera", y = "Actual Genera", fill = "Count") +
  theme_minimal(base_size = 10) +
  coord_equal()    

p

#(2c) Unique versus non-unique compounds
#After adding fingerprints
#Read files
importance_df <- read_csv("importance_all_ranks_fp.csv")
unique_df     <- read_csv("unique_compounds.csv")
#Define "important" compounds based on coefficient
top_imp <- importance_df %>%
  group_by(Rank) %>%
  arrange(desc(Importance_permutation)) %>%
  slice_head(n = 400) %>%
  ungroup()
#Count overlap with unique compounds
merged <- top_imp %>%
  left_join(unique_df %>% select(Feature, Rank) %>% mutate(Unique = 1),
            by = c("Feature", "Rank")) %>%
  mutate(Unique = ifelse(is.na(Unique), 0, Unique))
merged <- merged %>%
  mutate(Rank = factor(Rank, levels = c("Order", "Family", "Genus")))

#Scatter plots
p<- ggplot(merged, aes(x=Importance_permutation, y=Unique, color=factor(Unique))) +
  geom_point(shape = 21, fill = "white", size = 2, stroke = 0.6) +
  geom_vline(xintercept = 0, color = "black", linetype = "dashed", linewidth = 0.4) +
  facet_wrap(~Rank) +   
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 5),
    axis.text.y = element_text(size = 5),
    axis.title.x = element_text(size = 6, face = "bold"),
    axis.title.y = element_text(size = 6, face = "bold"),
    plot.title = element_text(size = 8, face = "bold"),
    panel.grid = element_blank(),
    panel.border = element_blank(),
    axis.line = element_line(color = "black", linewidth = 0.5),
    axis.ticks = element_line(color = "black", linewidth = 0.3),
    axis.ticks.length = unit(0.1, "cm")
  ) +
  labs(y = "Unique (1) vs Non-unique (0)", x = "Feature Importance")

p
```


Part 3: Plant species-metabolite relationship

```{r}
#Load libraries
library(dplyr)
library(vegan)
library(ape)      
library(readr) 
library(dendextend)
library(colorspace)
```


```{r}
#(3a) Mantel's test
#Genetic tree preparation

#Prepare tree and calculate genetic distance
ML_tree <- read.tree("Max_likelihood_tree.nex")
tips_to_remove <- c("Origanum_majorana", "Typhonium_sp", "Pyrus_communis", "Ocimum_tenuiflorum","Chloranthus_spicatus","Santalum_album")  

#Drop the specified tips
ML_tree_all <- drop.tip(ML_tree, tips_to_remove)
GenDist <- cophenetic.phylo(ML_tree_all)

#Chemical data preparation
#Prepare the chemical data
Chem_table<-read.csv("TreeTaxa_IndComp.csv", header = T, check.names = F)

#Removing taxa not present in the tree
All_Chem_table<-Chem_table[-c(1:4,70,234,270,284),]

#Check if tree tips match chem table taxa
identical(names(All_Chem_table$Taxa_Tips), ML_tree_all$tip.label) 
setequal(All_Chem_table$Taxa_Tips, ML_tree_all$tip.label)

#Remove columns where the sum is zero
str(All_Chem_table)
All_Chem_table <- All_Chem_table %>%
  mutate(across(-c(1:3), as.numeric))
keep_cols <- c(rep(TRUE, 3),                     
               colSums(All_Chem_table[, -c(1:3)]) > 0)

All_Chem_table <- All_Chem_table[, keep_cols]

#Chemical distance calculation
#Compute Jaccard distance
All_Chem_table <- All_Chem_table[match(rownames(GenDist), All_Chem_table$Taxa_Tips), ]
binary_dist <- vegdist(All_Chem_table[, -c(1:3)], method = "jaccard", binary = TRUE)

#Convert distance object to matrix
binary_dist_matrix <- as.matrix(binary_dist)

#Add species names as row and column names
rownames(binary_dist_matrix) <- All_Chem_table$Taxa_Tips
colnames(binary_dist_matrix) <- All_Chem_table$Taxa_Tips

#Running Mantel's test
set.seed(1234)
mantel_result <- mantel(binary_dist_matrix, GenDist, method = "spearman", permutations = 999)
print(mantel_result)

#(3b) UPGMA Dendrogram with chemical data
dist_mat <- as.matrix(binary_dist_matrix)
diag(dist_mat) <- 0                       
my_dist <- as.dist(binary_dist_matrix)               
hc <- hclust(my_dist, method = "average")  
tree <- as.phylo(hc)

#Comparison between Chemogram and Phylogeny
#Baker's gamma co-efficient calculation
# Read the tree file (replace 'your_tree_file.tree' with your actual file path)
tree <- read.nexus("Run12345_MCC.tree")
# Specify the tips to remove
tips_to_remove <- c("Origanum_majorana", "Typhonium_sp", "Pyrus_communis", "Ocimum_tenuiflorum","Chloranthus_spicatus","Santalum_album")  
# Drop the specified tips
tree_2 <- drop.tip(tree, tips_to_remove)


chem_dend   <- as.dendrogram(tree)        
gene_dend   <- as.dendrogram(tree_2)

bgamma <- cor_bakers_gamma(chem_dend, gene_dend)

#Calculate p-value
set.seed(123)                      
B     <- 99                      
perm  <- replicate(B, {
  perm_gene <- sample.dendrogram(gene_dend, replace = FALSE)  
  cor_bakers_gamma(chem_dend, perm_gene)
})

p_val <- (sum(abs(perm) >= abs(bgamma)) + 1) / (B + 1)  

#Tanglegram generation
chem_dend <- set(chem_dend, "branches_lwd", 0.6)
gene_dend <- set(gene_dend, "branches_lwd", 0.6)

#Untangle to cut down edge crossings
dl<- dendlist(chem_dend, gene_dend)
#1
dl<- untangle(dl, method = "step2side")  
entanglement(dl)  

#2
dl<- untangle(dl, method = "step1side")  
entanglement(dl) 

#Plot
p<-tanglegram(dl[[1]], dl[[2]],
           sort = FALSE,                        
           common_subtrees_color_lines = TRUE,  
           highlight_distinct_edges = FALSE,    
           columns_width = c(4, 1, 4),          
           margin_inner = 3,                    
           lwd = 0.8,                           
           lab.cex = 0.28,                      
           lab.col = "black",
           main = "Chemogram vs Genetic Phylogeny (311 taxa)")

p
```


Part 4: Calculation of phylogenetic signals

Note: The labels for the metabolite clusters that correspond to labels given in the images in the manuscript are as follows:

EXT_structural classes: 
M0 = PM1a = Sesquiterpene dominated
M1 = PM3a = Aliphatics and C5 branched chain dominated
M2 = PM2 = Simple benzenoids and phenylpropanoids + aromatic N and S compounds dominated
M3 = PM3b = Aliphatics and C5 branched chain dominated
M4 = PM1b = Monoterpene dominated
M5 = PM3c = Non-aromatic N and S compounds dominated + Aliphatics and C5 branched chain dominated  

EXT_biosynthetic classes:
M0 = PM1 = Terpenoid dominated
M1 = PM2 = Shikimate-derived aromatics dominated
M2 = PM3 = Fatty acid derivative dominated

```{r}
# Load packages
library(ape)
library(writexl)
library(phytools)
library(maps)
library(geiger)
library(phangorn)
library(mvtnorm)
library(MASS)
library(caper)
library(dplyr)
```


```{r}
# Read the tree file (replace 'your_tree_file.tree' with your actual file path)
tree <- read.nexus("Run12345_MCC.tree")
# Specify the tips to remove
tips_to_remove <- c("Origanum_majorana", "Typhonium_sp", "Pyrus_communis", "Ocimum_tenuiflorum","Chloranthus_spicatus","Santalum_album")  
# Drop the specified tips
tree_2 <- drop.tip(tree, tips_to_remove)
```

Whole tree

EXT_structural classes
```{r}
EXT_str<-read.csv("cluster_binary_EXT_str.csv", header = T, check.names = F)
#Remove chloranthales and santalales
EXT_str_whole2 <- EXT_str %>% filter(!Order %in% c("Chloranthales", "Santalales"))

#Check if the matrix and tree tips match
identical(sort(tree_2$tip.label), sort(EXT_str_whole2$Taxa_Tips)) 

#Calculation of D-stats
physig <- comparative.data(tree_2, EXT_str_whole2, names.col = "Taxa_Tips", vcv = TRUE, warn.dropped = TRUE)
```

M0 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M0, permut = 1000)
print(phylo_D_result)
```

M1 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M1, permut = 1000)
print(phylo_D_result)
```

M2 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M2, permut = 1000)
print(phylo_D_result)
```

M3 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M3, permut = 1000)
print(phylo_D_result)
```

M4 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M4, permut = 1000)
print(phylo_D_result)
```

M5 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M5, permut = 1000)
print(phylo_D_result)
```

EXT_biosynthetic classes
```{r}
EXT_bio<-read.csv("cluster_binary_EXT_bio.csv", header = T, check.names = F)
#Remove chloranthales and santalales
EXT_bio_whole2 <- EXT_bio %>% filter(!Order %in% c("Chloranthales", "Santalales"))
```

Check if the matrix and tree tips match
```{r}
identical(sort(tree_2$tip.label), sort(EXT_bio_whole2$Taxa_Tips)) 
```

Calculation of D-stats
```{r}
physig <- comparative.data(tree_2, EXT_bio_whole2, names.col = "Taxa_Tips", vcv = TRUE, warn.dropped = TRUE)
```

M0 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M0, permut = 1000)
print(phylo_D_result)
```

M1 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M1, permut = 1000)
print(phylo_D_result)
```

M2 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M2, permut = 1000)
print(phylo_D_result)
```

Rosids
```{r}
#Specify the tips to keep
tips_to_keep <- c("Acacia_caven","Aesculus_hippocastanum","Anacardium_occidentale","Backhousia_citriodora",        "Bauhinia_sp","Boswellia_sp","Brassica_rapa","Bruguiera_gymnorrhiza","Callistemon_citrinus","Callistemon_viminalis",         "Causonia_japonica","Ceiba_pentandra","Chukrasia_tabularis","Cistus_ladanifer","Citrus_limon",                "Corymbia_citriodora","Daphne_mezereum","Dictamnus_albus","Eucalyptus_alba","Eucalyptus_camaldulensis",      "Eucalyptus_deglupta","Eucalyptus_globulus","Eucalyptus_propinqua","Eucalyptus_robusta","Eucalyptus_saligna",            "Eucalyptus_tereticornis","Eucalyptus_urophylla","Eugenia_uniflora","Ficus_aurata","Ficus_beccarii",              "Ficus_benjamina","Ficus_condensa","Ficus_crassiramea","Ficus_deltoidea","Ficus_fulva","Ficus_megaleia",             "Ficus_microcarpa","Ficus_obscura","Ficus_punctata","Ficus_stolonifera","Geranium_macrorrhizum","Geranium_phaeum",         "Glycyrrhiza_echinata","Glycyrrhiza_glabra","Glycyrrhiza_inflata","Hibiscus_sp","Hypericum_barbatum",            "Hypericum_hirsutum","Hypericum_linarioides","Hypericum_maculatum","Hypericum_olympicum","Hypericum_perforatum",          "Hypericum_richeri_grisebachii","Hypericum_rumeliacum","Hypericum_tetrapterum","Inga_marginata",               "Kandelia_candel","Lathyrus_odoratus","Lawsonia_inermis","Lumnitzera_racemosa","Malus_domestica",              "Mangifera_indica","Melaleuca_sp","Murraya_koenigii","Myrtus_communis","Naregamia_alata",            "Pelargonium_endlicherianum","Pelargonium_graveolens","Pemphis_acidula","Pistacia_vera","Prunus_armeniaca",             "Prunus_avium","Prunus_domestica","Prunus_padus","Prunus_persica","Rhizophora_stylosa","Rosa_chinensis",                "Rosa_gallica","Rosa_odorata_gigantea","Salix_caprea","Salix_cinerea","Salix_repens_rosmarinifolia","Schinus_molle",        "Sonneratia_alba","Tilia_sp","Viola_etrusca","Viola_odorata","Vitis_vinifera")
#Drop the specified tips
tree_rosids <- keep.tip(tree, tips_to_keep)
```

EXT_structural classes
```{r}
#Keep Rosids
selected_orders <- c("Fabales","Rosales","Malpighiales","Geraniales","Myrtales","Malvales","Brassicales","Sapindales","Vitales")
EXT_str_rosids <- EXT_str %>% filter(Order %in% selected_orders)
unique(EXT_str_rosids$Taxa_Tips)
```

Check if the matrix and tree tips match
```{r}
identical(sort(tree_rosids$tip.label), sort(EXT_str_rosids$Taxa_Tips)) 
```

Calculation of D-stats
```{r}
physig <- comparative.data(tree_rosids, EXT_str_rosids, names.col = "Taxa_Tips", vcv = TRUE, warn.dropped = TRUE)
```

M0 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M0, permut = 1000)
print(phylo_D_result)
```

M1 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M1, permut = 1000)
print(phylo_D_result)
```

M2 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M2, permut = 1000)
print(phylo_D_result)
```

M3 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M3, permut = 1000)
print(phylo_D_result)
```

M4 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M4, permut = 1000)
print(phylo_D_result)
```

M5 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M5, permut = 1000)
print(phylo_D_result)
```

EXT_biosynthetic classes
```{r}
#Keep Rosids
selected_orders <- c("Fabales","Rosales","Malpighiales","Geraniales","Myrtales","Malvales","Brassicales","Sapindales","Vitales")
EXT_bio_rosids <- EXT_bio %>% filter(Order %in% selected_orders)
```

Check if the matrix and tree tips match
```{r}
identical(sort(tree_rosids$tip.label), sort(EXT_bio_rosids$Taxa_Tips))
```

Calculation of D-stats
```{r}
physig <- comparative.data(tree_rosids, EXT_bio_rosids, names.col = "Taxa_Tips", vcv = TRUE, warn.dropped = TRUE)
```

M0 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M0, permut = 1000)
print(phylo_D_result)
```

M1 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M1, permut = 1000)
print(phylo_D_result)
```

M2 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M2, permut = 1000)
print(phylo_D_result)
```

Asterids
```{r}
# Specify the tips to keep
tips_to_keep <- c("Achillea_ageratum","Achillea_millefolium","Acnistus_arborescens","Actinidia_chinensis",        "Ageratum_conyzoides","Allamanda_cathartica","Aloysia_citriodora","Aloysia_triphylla","Anaphalis_contorta",        "Anethuum_graveolens","Angelica_sylvestris","Anthriscus_cerefolium","Antirrhinum_majus","Apium_graveolens",           "Arnica_montana","Artemisia_annua","Avicennia_marina","Bartsia_alpinia","Calendula_officinalis","Carduus_pycnocephalus", "Carum_carvi","Caryopteris_sp","Catharanthus_roseus","Centaurea_armena","Centaurea_depressa","Centella_asiatica",          "Centratherum_punctatum","Chamaemelum_nobile","Chrysactinia_mexicana","Chrysanthemum_coronarium","Clinopodium_vulgare",  "Conopodium_majus","Coriandrum_sativum","Couroupita_guianensis","Crassocephalum_crepidiodes","Crithmum_maritimum",        "Cuminum_cyminum","Cyclamen_persicum","Cyclamen_purpurascens","Dracocephalum_moldavica","Elsholtzia_blanda",          "Elsholtzia_ciliata","Elsholtzia_densa","Elsholtzia_fruticosa","Exacum_affine","Foeniculum_vulgare",        "Gallium_aparine","Galium_odoratum","Gymnema_sylvestre","Heliotropium_myosotifolium","Heliotropium_pycnophyllum", "Heliotropium_stenophyllum","Hyssopus_officinalis","Jasminum_sp","Lavandula_angustifolia","Lecythis_persistens",        "Leontopodium_alpinum","Levisticum_officinale","Ligustrum_japonicum","Lippia_alba","Lonicera_japonica",          "Marrubium_peregrinum","Marrubium_vulgare","Matricaria_chamomilla","Matricara_recutita","Melissa_officinalis",       "Mentha_arvensis","Mentha_canadensis","Mentha_longifolia","Mentha_spicata","Meum_athamanticum","Mikania_glomerata",         "Monarda_citriodora","Monardo_didyma","Nepeta_cataria","Nyctanthes_arbortristis","Ocimum_americanum",         "Ocimum_basilicum","Oenanthe_crocata","Olea_europaea","Oliveria_decumbens","Origanum_vulgare","Parkia_biglobosa",           "Petroselinum_crispum","Phlox_sp","Pimpinella_saxifraga","Plantago_ovata","Plumeria_rubra","Pogostemon_cablin",         "Posoqueria_latifolia","Rosamarinus_officinalis","Salvia_fruticosa","Salvia_officinalis","Salvia_sclarea",             "Satureja_hortensis","Saussurea_costus","Stachys_byzantina","Syringa_oblata","Tagetes_minuta",         "Tanacetum_parthenium","Thevetia_peruviana","Thymus_pulegiodes","Thymus_vulgaris","Valeriana_jatamansi")
# Drop the specified tips
tree_asterids <- keep.tip(tree, tips_to_keep)
```

EXT_structural classes
```{r}
#Keep Asterids
selected_orders <- c("Ericales","Asterales","Apiales","Dipsacales","Solanales","Lamiales","Gentianales","Boraginales")
EXT_str_asterids <- EXT_str %>% filter(Order %in% selected_orders)
unique(EXT_str_asterids$Taxa_Tips)
```

Check if the matrix and tree tips match
```{r}
identical(sort(tree_asterids$tip.label), sort(EXT_str_asterids$Taxa_Tips)) 
```

Calculation of D-stats
```{r}
physig <- comparative.data(tree_asterids, EXT_str_asterids, names.col = "Taxa_Tips", vcv = TRUE, warn.dropped = TRUE)
```

M0 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M0, permut = 1000)
print(phylo_D_result)
```

M1 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M1, permut = 1000)
print(phylo_D_result)
```

M2 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M2, permut = 1000)
print(phylo_D_result)
```

M3 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M3, permut = 1000)
print(phylo_D_result)
```

M4 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M4, permut = 1000)
print(phylo_D_result)
```

M5 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M5, permut = 1000)
print(phylo_D_result)
```

EXT_biosynthetic classes
```{r}
#Keep Asterids
selected_orders <- c("Ericales","Asterales","Apiales","Dipsacales","Solanales","Lamiales","Gentianales","Boraginales")
EXT_bio_asterids <- EXT_bio %>% filter(Order %in% selected_orders)
```

Check if the matrix and tree tips match
```{r}
identical(sort(tree_asterids$tip.label), sort(EXT_bio_asterids$Taxa_Tips)) 
```

Calculation of D-stats
```{r}
physig <- comparative.data(tree_asterids, EXT_bio_asterids, names.col = "Taxa_Tips", vcv = TRUE, warn.dropped = TRUE)
```

M0 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M0, permut = 1000)
print(phylo_D_result)
```

M1 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M1, permut = 1000)
print(phylo_D_result)
```

M2 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M2, permut = 1000)
print(phylo_D_result)
```

Malvids
```{r}
# Specify the tips to keep
tips_to_keep <- c("Aesculus_hippocastanum","Anacardium_occidentale","Backhousia_citriodora","Boswellia_sp",               "Brassica_rapa","Callistemon_citrinus","Callistemon_viminalis","Ceiba_pentandra","Chukrasia_tabularis",      "Cistus_ladanifer","Citrus_limon","Corymbia_citriodora","Daphne_mezereum","Dictamnus_albus","Eucalyptus_alba",           "Eucalyptus_camaldulensis","Eucalyptus_deglupta","Eucalyptus_globulus","Eucalyptus_propinqua","Eucalyptus_robusta",         "Eucalyptus_saligna","Eucalyptus_tereticornis","Eucalyptus_urophylla","Eugenia_uniflora","Geranium_macrorrhizum",     "Geranium_phaeum","Hibiscus_sp","Lawsonia_inermis","Lumnitzera_racemosa","Mangifera_indica","Melaleuca_sp",               "Murraya_koenigii","Myrtus_communis","Naregamia_alata","Pelargonium_endlicherianum","Pelargonium_graveolens",   "Pemphis_acidula","Pistacia_vera","Schinus_molle","Sonneratia_alba","Tilia_sp")
# Drop the specified tips
tree_malvids <- keep.tip(tree, tips_to_keep)
```

EXT_structural classes
```{r}
selected_orders <- c("Geraniales","Myrtales","Malvales","Brassicales","Sapindales")
EXT_str_malvids <- EXT_str %>% filter(Order %in% selected_orders)
unique(EXT_str_malvids$Taxa_Tips)
```

Check if the matrix and tree tips match
```{r}
identical(sort(tree_malvids$tip.label), sort(EXT_str_malvids$Taxa_Tips)) 
```

Calculation of D-stats
```{r}
physig <- comparative.data(tree_malvids, EXT_str_malvids, names.col = "Taxa_Tips", vcv = TRUE, warn.dropped = TRUE)
```

M0 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M0, permut = 1000)
print(phylo_D_result)
```

M1 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M1, permut = 1000)
print(phylo_D_result)
```

M2 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M2, permut = 1000)
print(phylo_D_result)
```

M3 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M3, permut = 1000)
print(phylo_D_result)
```

M4 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M4, permut = 1000)
print(phylo_D_result)
```

M5 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M5, permut = 1000)
print(phylo_D_result)
```

EXT_biosynthetic classes
```{r}
selected_orders <- c("Geraniales","Myrtales","Malvales","Brassicales","Sapindales")
EXT_bio_malvids <- EXT_bio %>% filter(Order %in% selected_orders)
```

Check if the matrix and tree tips match
```{r}
identical(sort(tree_malvids$tip.label), sort(EXT_bio_malvids$Taxa_Tips)) 
```

Calculation of D-stats
```{r}
physig <- comparative.data(tree_malvids, EXT_bio_malvids, names.col = "Taxa_Tips", vcv = TRUE, warn.dropped = TRUE)
```

M0 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M0, permut = 1000)
print(phylo_D_result)
```

M1 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M1, permut = 1000)
print(phylo_D_result)
```

M2 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M2, permut = 1000)
print(phylo_D_result)
```

Fabids
```{r}
# Specify the tips to keep
tips_to_keep <- c("Acacia_caven","Bauhinia_sp","Bruguiera_gymnorrhiza","Ficus_aurata","Ficus_beccarii",               "Ficus_benjamina","Ficus_condensa","Ficus_crassiramea","Ficus_deltoidea","Ficus_fulva","Ficus_megaleia",               "Ficus_microcarpa","Ficus_obscura","Ficus_punctata","Ficus_stolonifera","Glycyrrhiza_echinata","Glycyrrhiza_glabra",     "Glycyrrhiza_inflata","Hypericum_barbatum","Hypericum_hirsutum","Hypericum_linarioides","Hypericum_maculatum",           "Hypericum_olympicum","Hypericum_perforatum","Hypericum_richeri_grisebachii","Hypericum_rumeliacum",          "Hypericum_tetrapterum","Inga_marginata","Kandelia_candel","Lathyrus_odoratus","Malus_domestica",               "Prunus_armeniaca","Prunus_avium","Prunus_domestica","Prunus_padus","Prunus_persica","Rhizophora_stylosa",           "Rosa_chinensis","Rosa_gallica","Rosa_odorata_gigantea","Salix_caprea","Salix_cinerea",            "Salix_repens_rosmarinifolia","Viola_etrusca","Viola_odorata")
# Drop the specified tips
tree_fabids <- keep.tip(tree, tips_to_keep)
```

EXT_structural classes
```{r}
selected_orders <- c("Fabales","Rosales","Malpighiales")
EXT_str_fabids <- EXT_str %>% filter(Order %in% selected_orders)
unique(EXT_str_fabids$Taxa_Tips)
```

Check if the matrix and tree tips match
```{r}
identical(sort(tree_fabids$tip.label), sort(EXT_str_fabids$Taxa_Tips)) 
```

Calculation of D-stats
```{r}
physig <- comparative.data(tree_fabids, EXT_str_fabids, names.col = "Taxa_Tips", vcv = TRUE, warn.dropped = TRUE)
```

M0 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M0, permut = 1000)
print(phylo_D_result)
```

M1 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M1, permut = 1000)
print(phylo_D_result)
```

M2 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M2, permut = 1000)
print(phylo_D_result)
```

M3 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M3, permut = 1000)
print(phylo_D_result)
```

M4 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M4, permut = 1000)
print(phylo_D_result)
```

M5 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M5, permut = 1000)
print(phylo_D_result)
```

EXT_biosynthetic classes
```{r}
selected_orders <- c("Fabales","Rosales","Malpighiales")
EXT_bio_fabids <- EXT_bio %>% filter(Order %in% selected_orders)
```

Check if the matrix and tree tips match
```{r}
identical(sort(tree_fabids$tip.label), sort(EXT_bio_fabids$Taxa_Tips)) 
```

Calculation of D-stats
```{r}
physig <- comparative.data(tree_fabids, EXT_bio_fabids, names.col = "Taxa_Tips", vcv = TRUE, warn.dropped = TRUE)
```

M0 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M0, permut = 1000)
print(phylo_D_result)
```

M1 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M1, permut = 1000)
print(phylo_D_result)
```

M2 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M2, permut = 1000)
print(phylo_D_result)
```

Lamids
```{r}
# Specify the tips to keep
tips_to_keep <- c("Acnistus_arborescens","Allamanda_cathartica","Aloysia_citriodora","Aloysia_triphylla",          "Antirrhinum_majus","Avicennia_marina","Bartsia_alpinia","Caryopteris_sp","Catharanthus_roseus","Clinopodium_vulgare",   "Dracocephalum_moldavica","Elsholtzia_blanda","Elsholtzia_ciliata","Elsholtzia_densa","Elsholtzia_fruticosa",     "Exacum_affine","Gallium_aparine","Galium_odoratum","Gymnema_sylvestre","Heliotropium_myosotifolium","Heliotropium_pycnophyllum","Heliotropium_stenophyllum","Hyssopus_officinalis","Jasminum_sp","Lavandula_angustifolia","Ligustrum_japonicum",        "Lippia_alba","Marrubium_peregrinum","Marrubium_vulgare","Melissa_officinalis","Mentha_arvensis",        "Mentha_canadensis","Mentha_longifolia","Mentha_spicata","Monarda_citriodora","Monardo_didyma","Nepeta_cataria",            "Nyctanthes_arbortristis","Ocimum_americanum","Ocimum_basilicum","Olea_europaea","Origanum_vulgare",          "Parkia_biglobosa","Plantago_ovata","Plumeria_rubra","Pogostemon_cablin","Posoqueria_latifolia","Rosamarinus_officinalis","Salvia_fruticosa","Salvia_officinalis","Salvia_sclarea","Satureja_hortensis","Stachys_byzantina","Syringa_oblata",       "Thevetia_peruviana","Thymus_pulegiodes","Thymus_vulgaris")
# Drop the specified tips
tree_lamids <- keep.tip(tree, tips_to_keep)
```

EXT_structural classes
```{r}
selected_orders <- c("Solanales","Lamiales","Gentianales","Boraginales")
EXT_str_lamids <- EXT_str %>% filter(Order %in% selected_orders)
unique(EXT_str_lamids$Taxa_Tips)
```

Check if the matrix and tree tips match
```{r}
identical(sort(tree_lamids$tip.label), sort(EXT_str_lamids$Taxa_Tips)) 
```

Calculation of D-stats
```{r}
physig <- comparative.data(tree_lamids, EXT_str_lamids, names.col = "Taxa_Tips", vcv = TRUE, warn.dropped = TRUE)
```

M0 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M0, permut = 1000)
print(phylo_D_result)
```

M1 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M1, permut = 1000)
print(phylo_D_result)
```

M2 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M2, permut = 1000)
print(phylo_D_result)
```

M3 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M3, permut = 1000)
print(phylo_D_result)
```

M4 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M4, permut = 1000)
print(phylo_D_result)
```

M5 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M5, permut = 1000)
print(phylo_D_result)
```

EXT_biosynthetic classes
```{r}
selected_orders <- c("Solanales","Lamiales","Gentianales","Boraginales")
EXT_bio_lamids <- EXT_bio %>% filter(Order %in% selected_orders)
```

Check if the matrix and tree tips match
```{r}
identical(sort(tree_lamids$tip.label), sort(EXT_bio_lamids$Taxa_Tips)) 
```

Calculation of D-stats
```{r}
physig <- comparative.data(tree_lamids, EXT_bio_lamids, names.col = "Taxa_Tips", vcv = TRUE, warn.dropped = TRUE)
```

M0 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M0, permut = 1000)
print(phylo_D_result)
```

M1 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M1, permut = 1000)
print(phylo_D_result)
```

M2 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M2, permut = 1000)
print(phylo_D_result)
```

Campanuliids
```{r}
# Specify the tips to keep
tips_to_keep <- c("Achillea_ageratum","Achillea_millefolium","Ageratum_conyzoides","Anaphalis_contorta",        "Anethuum_graveolens","Angelica_sylvestris","Anthriscus_cerefolium","Apium_graveolens","Arnica_montana",            "Artemisia_annua","Calendula_officinalis","Carduus_pycnocephalus","Carum_carvi","Centaurea_armena",       "Centaurea_depressa","Centella_asiatica","Centratherum_punctatum","Chamaemelum_nobile","Chrysactinia_mexicana",      "Chrysanthemum_coronarium","Conopodium_majus","Coriandrum_sativum","Crassocephalum_crepidiodes","Crithmum_maritimum",    "Cuminum_cyminum","Foeniculum_vulgare","Leontopodium_alpinum","Levisticum_officinale","Lonicera_japonica",      "Matricaria_chamomilla","Matricara_recutita","Meum_athamanticum","Mikania_glomerata","Oenanthe_crocata",        "Oliveria_decumbens","Petroselinum_crispum","Pimpinella_saxifraga","Saussurea_costus","Tagetes_minuta",        "Tanacetum_parthenium","Valeriana_jatamansi")
# Drop the specified tips
tree_campanuliids <- keep.tip(tree, tips_to_keep)
```

EXT_structural classes
```{r}
selected_orders <- c("Asterales","Dipsacales","Apiales")
EXT_str_campanuliids <- EXT_str %>% filter(Order %in% selected_orders)
unique(EXT_str_campanuliids$Taxa_Tips)
```

Check if the matrix and tree tips match
```{r}
identical(sort(tree_campanuliids$tip.label), sort(EXT_str_campanuliids$Taxa_Tips)) 
```

Calculation of D-stats
```{r}
physig <- comparative.data(tree_campanuliids, EXT_str_campanuliids, names.col = "Taxa_Tips", vcv = TRUE, warn.dropped = TRUE)
```

M0 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M0, permut = 1000)
print(phylo_D_result)
```

M1 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M1, permut = 1000)
print(phylo_D_result)
```

M2 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M2, permut = 1000)
print(phylo_D_result)
```

M3 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M3, permut = 1000)
print(phylo_D_result)
```

M4 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M4, permut = 1000)
print(phylo_D_result)
```

M5 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M5, permut = 1000)
print(phylo_D_result)
```

EXT_biosynthetic classes
```{r}
selected_orders <- c("Asterales","Dipsacales","Apiales")
EXT_bio_campanuliids <- EXT_bio %>% filter(Order %in% selected_orders)
```

Check if the matrix and tree tips match
```{r}
identical(sort(tree_campanuliids$tip.label), sort(EXT_bio_campanuliids$Taxa_Tips)) 
```

Calculation of D-stats
```{r}
physig <- comparative.data(tree_campanuliids, EXT_bio_campanuliids, names.col = "Taxa_Tips", vcv = TRUE, warn.dropped = TRUE)
```

M0 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M0, permut = 1000)
print(phylo_D_result) #Has single state
```

M1 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M1, permut = 1000)
print(phylo_D_result) 
```

M2 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M2, permut = 1000)
print(phylo_D_result) 
```

Commelinids
```{r}
# Specify the tips to keep
tips_to_keep <- c("Aframomum_sp","Alpinia_galanga","Alpinia_purpurata","Alpinia_zerumbet","Ammandra_decasperma",       "Amomum_subulatum","Aphandra_natalia","Chrysopogon_nigritanus","Chrysopogon_zizanioides","Cymbopogon_citratus",       "Cymbopogon_flexuosus","Cymbopogon_martinii","Cymbopogon_nardus","Cymbopogon_winterianus","Cyperus_articulatus",       "Cyperus_rotundus","Hedychium_coccineum","Hedychium_coronarium","Hedychium_flavescens","Hedychium_gardnerianum", "Nypa_fruticans","Phytelephas_aequatorialis","Phytelephas_macrocarpa","Phytelephas_seemannii","Zingiber_officinale",       "Zingiber_zerumbet")
# Drop the specified tips
tree_commelinids <- keep.tip(tree, tips_to_keep)
```

EXT_structural classes
```{r}
selected_orders <- c("Arecales","Poales","Commelinales","Zingiberales")
EXT_str_commelinids <- EXT_str %>% filter(Order %in% selected_orders)
unique(EXT_str_commelinids$Taxa_Tips)
```

Check if the matrix and tree tips match
```{r}
identical(sort(tree_commelinids$tip.label), sort(EXT_str_commelinids$Taxa_Tips))
```

Calculation of D-stats
```{r}
physig <- comparative.data(tree_commelinids, EXT_str_commelinids, names.col = "Taxa_Tips", vcv = TRUE, warn.dropped = TRUE)
```

M0 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M0, permut = 1000)
print(phylo_D_result) #Has a single state
```

M1 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M1, permut = 1000)
print(phylo_D_result) 
```

M2 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M2, permut = 1000)
print(phylo_D_result) 
```

M3 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M3, permut = 1000)
print(phylo_D_result) 
```

M4 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M4, permut = 1000)
print(phylo_D_result) 
```

M5 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M5, permut = 1000)
print(phylo_D_result) 
```

EXT_biosynthetic classes
```{r}
selected_orders <- c("Arecales","Poales","Commelinales","Zingiberales")
EXT_bio_commelinids <- EXT_bio %>% filter(Order %in% selected_orders)
```

Check if the matrix and tree tips match
```{r}
identical(sort(tree_commelinids$tip.label), sort(EXT_bio_commelinids$Taxa_Tips)) 
```

Calculation of D-stats
```{r}
physig <- comparative.data(tree_commelinids, EXT_bio_commelinids, names.col = "Taxa_Tips", vcv = TRUE, warn.dropped = TRUE)
```

M0 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M0, permut = 1000)
print(phylo_D_result) #Single state
```

M1 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M1, permut = 1000)
print(phylo_D_result) 
```

M2 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M2, permut = 1000)
print(phylo_D_result) 
```

Magnoliids
```{r}
# Specify the tips to keep
tips_to_keep <- c("Annona_sp","Bubbia_sp","Cananga_odorata","Cassytha_filiformis","Cinnamomum_verum",        "Eupomatia_laurina","Exospermum_stipitatum","Laurus_nobilis","Liriodendron_chinensis","Liriodendron_tulipifera", "Litsea_cubeba","Magnolia_acuminata","Magnolia_denudata","Magnolia_figo","Magnolia_grandiflora","Magnolia_obovata",       "Magnolia_salicifolia","Magnolia_tomentosa","Magnolia_tripetala","Magnolia_virginiana","Myristica_fragrans",      "Ocotea_meziana","Ocotea_sinuata","Ocotea_valeriana","Ocotea_veraguensis","Piper_auritum","Xylopia_sp",           "Zygogynum_baillonii","Zygogynum_bicolor","Zygogynum_pomiferum" )
# Drop the specified tips
tree_magnoliids <- keep.tip(tree, tips_to_keep)
```

EXT_structural classes
```{r}
selected_orders <- c("Magnoliales","Laurales","Piperales","Canellales")
EXT_str_magnoliids <- EXT_str %>% filter(Order %in% selected_orders)
unique(EXT_str_magnoliids$Taxa_Tips)
```

Check if the matrix and tree tips match
```{r}
identical(sort(tree_magnoliids$tip.label), sort(EXT_str_magnoliids$Taxa_Tips)) 
```

Calculation of D-stats
```{r}
physig <- comparative.data(tree_magnoliids, EXT_str_magnoliids, names.col = "Taxa_Tips", vcv = TRUE, warn.dropped = TRUE)
```

M0 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M0, permut = 1000)
print(phylo_D_result)
```

M1 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M1, permut = 1000)
print(phylo_D_result)
```

M2 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M2, permut = 1000)
print(phylo_D_result)
```

M3 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M3, permut = 1000)
print(phylo_D_result)
```

M4 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M4, permut = 1000)
print(phylo_D_result)
```

M5 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M5, permut = 1000)
print(phylo_D_result)
```

EXT_biosynthetic classes
```{r}
selected_orders <- c("Magnoliales","Laurales","Piperales","Canellales")
EXT_bio_magnoliids <- EXT_bio %>% filter(Order %in% selected_orders)
```

Check if the matrix and tree tips match
```{r}
identical(sort(tree_magnoliids$tip.label), sort(EXT_bio_magnoliids$Taxa_Tips)) 
```

Calculation of D-stats
```{r}
physig <- comparative.data(tree_magnoliids, EXT_bio_magnoliids, names.col = "Taxa_Tips", vcv = TRUE, warn.dropped = TRUE)
```

M0 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M0, permut = 1000)
print(phylo_D_result)
```

M1 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M1, permut = 1000)
print(phylo_D_result)
```

M2 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M2, permut = 1000)
print(phylo_D_result)
```

Myrtales
```{r}
# Specify the tips to keep
tips_to_keep <- c("Backhousia_citriodora","Callistemon_citrinus","Callistemon_viminalis","Corymbia_citriodora",     "Eucalyptus_alba","Eucalyptus_camaldulensis","Eucalyptus_deglupta","Eucalyptus_globulus","Eucalyptus_propinqua",     "Eucalyptus_robusta","Eucalyptus_saligna","Eucalyptus_tereticornis","Eucalyptus_urophylla","Eugenia_uniflora",         "Lawsonia_inermis","Lumnitzera_racemosa","Melaleuca_sp","Myrtus_communis","Pemphis_acidula","Sonneratia_alba")
# Drop the specified tips
tree_myrtales <- keep.tip(tree, tips_to_keep)
```

EXT_structural classes
```{r}
selected_orders <- "Myrtales"
EXT_str_myrtales <- EXT_str %>% filter(Order %in% selected_orders)
unique(EXT_str_myrtales$Taxa_Tips)
```

Check if the matrix and tree tips match
```{r}
identical(sort(tree_myrtales$tip.label), sort(EXT_str_myrtales$Taxa_Tips)) 
```

Calculation of D-stats
```{r}
physig <- comparative.data(tree_myrtales,EXT_str_myrtales, names.col = "Taxa_Tips", vcv = TRUE, warn.dropped = TRUE)
```

M0 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M0, permut = 1000)
print(phylo_D_result)
```

M1 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M1, permut = 1000)
print(phylo_D_result)
```

M2 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M2, permut = 1000)
print(phylo_D_result)
```

M3 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M3, permut = 1000)
print(phylo_D_result)
```

M4 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M4, permut = 1000)
print(phylo_D_result)
```

M5 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M5, permut = 1000)
print(phylo_D_result)
```

EXT_biosynthetic classes
```{r}
selected_orders <- "Myrtales"
EXT_bio_myrtales <- EXT_bio %>% filter(Order %in% selected_orders)
```

Check if the matrix and tree tips match
```{r}
identical(sort(tree_myrtales$tip.label), sort(EXT_bio_myrtales$Taxa_Tips)) 
```

Calculation of D-stats
```{r}
physig <- comparative.data(tree_myrtales, EXT_bio_myrtales, names.col = "Taxa_Tips", vcv = TRUE, warn.dropped = TRUE)
```

M0 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M0, permut = 1000)
print(phylo_D_result) #Single state
```

M1 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M1, permut = 1000)
print(phylo_D_result)
```

M2 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M2, permut = 1000)
print(phylo_D_result) #Single state
```

Rosales
```{r}
# Specify the tips to keep
tips_to_keep <- c("Ficus_aurata","Ficus_beccarii","Ficus_benjamina","Ficus_condensa","Ficus_crassiramea",     "Ficus_deltoidea","Ficus_fulva","Ficus_megaleia","Ficus_microcarpa","Ficus_obscura","Ficus_punctata","Ficus_stolonifera", "Malus_domestica","Prunus_armeniaca","Prunus_avium","Prunus_domestica","Prunus_padus","Prunus_persica","Rosa_chinensis",  "Rosa_gallica","Rosa_odorata_gigantea")
# Drop the specified tips
tree_rosales <- keep.tip(tree, tips_to_keep)
```

EXT_structural classes
```{r}
selected_orders <- "Rosales"
EXT_str_rosales <- EXT_str %>% filter(Order %in% selected_orders)
unique(EXT_str_rosales$Taxa_Tips)
```

Check if the matrix and tree tips match
```{r}
identical(sort(tree_rosales$tip.label), sort(EXT_str_rosales$Taxa_Tips)) 
```

Calculation of D-stats
```{r}
physig <- comparative.data(tree_rosales, EXT_str_rosales, names.col = "Taxa_Tips", vcv = TRUE, warn.dropped = TRUE)
```

M0 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M0, permut = 1000)
print(phylo_D_result)
```

M1 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M1, permut = 1000)
print(phylo_D_result)
```

M2 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M2, permut = 1000)
print(phylo_D_result)
```

M3 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M3, permut = 1000)
print(phylo_D_result)
```

M4 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M4, permut = 1000)
print(phylo_D_result)
```

M5 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M5, permut = 1000)
print(phylo_D_result)
```

EXT_biosynthetic classes
```{r}
selected_orders <- "Rosales"
EXT_bio_rosales <- EXT_bio %>% filter(Order %in% selected_orders)
```

Check if the matrix and tree tips match
```{r}
identical(sort(tree_rosales$tip.label), sort(EXT_bio_rosales$Taxa_Tips)) 
```

Calculation of D-stats
```{r}
physig <- comparative.data(tree_rosales, EXT_bio_rosales, names.col = "Taxa_Tips", vcv = TRUE, warn.dropped = TRUE)
```

M0 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M0, permut = 1000)
print(phylo_D_result)
```

M1 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M1, permut = 1000)
print(phylo_D_result)
```

M2 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M2, permut = 1000)
print(phylo_D_result)
```

Lamiales
```{r}
# Specify the tips to keep
tips_to_keep <- c("Aloysia_citriodora","Aloysia_triphylla","Antirrhinum_majus","Avicennia_marina","Bartsia_alpinia",       "Caryopteris_sp","Clinopodium_vulgare","Dracocephalum_moldavica","Elsholtzia_blanda","Elsholtzia_ciliata",      "Elsholtzia_densa","Elsholtzia_fruticosa","Hyssopus_officinalis","Jasminum_sp","Lavandula_angustifolia",  "Ligustrum_japonicum","Lippia_alba","Marrubium_peregrinum","Marrubium_vulgare","Melissa_officinalis","Mentha_arvensis",  "Mentha_canadensis","Mentha_longifolia","Mentha_spicata","Monarda_citriodora","Monardo_didyma","Nepeta_cataria",          "Nyctanthes_arbortristis","Ocimum_americanum","Ocimum_basilicum","Olea_europaea","Origanum_vulgare","Parkia_biglobosa",   "Plantago_ovata","Pogostemon_cablin","Rosamarinus_officinalis","Salvia_fruticosa","Salvia_officinalis","Salvia_sclarea",  "Satureja_hortensis","Stachys_byzantina","Syringa_oblata","Thymus_pulegiodes","Thymus_vulgaris")
# Drop the specified tips
tree_lamiales <- keep.tip(tree, tips_to_keep)
```

EXT_structural classes
```{r}
selected_orders <- "Lamiales"
EXT_str_lamiales <- EXT_str %>% filter(Order %in% selected_orders)
unique(EXT_str_lamiales$Taxa_Tips)
```

Check if the matrix and tree tips match
```{r}
identical(sort(tree_lamiales$tip.label), sort(EXT_str_lamiales$Taxa_Tips)) 
```

Calculation of D-stats
```{r}
physig <- comparative.data(tree_lamiales, EXT_str_lamiales, names.col = "Taxa_Tips", vcv = TRUE, warn.dropped = TRUE)
```

M0 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M0, permut = 1000)
print(phylo_D_result)
```

M1 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M1, permut = 1000)
print(phylo_D_result)
```

M2 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M2, permut = 1000)
print(phylo_D_result)
```

M3 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M3, permut = 1000)
print(phylo_D_result)
```

M4 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M4, permut = 1000)
print(phylo_D_result)
```

M5 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M5, permut = 1000)
print(phylo_D_result)
```

EXT_biosynthetic classes
```{r}
selected_orders <- "Lamiales"
EXT_bio_lamiales <- EXT_bio %>% filter(Order %in% selected_orders)
```

Check if the matrix and tree tips match
```{r}
identical(sort(tree_lamiales$tip.label), sort(EXT_bio_lamiales$Taxa_Tips)) 
```

Calculation of D-stats
```{r}
physig <- comparative.data(tree_lamiales, EXT_bio_lamiales, names.col = "Taxa_Tips", vcv = TRUE, warn.dropped = TRUE)
```

M0 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M0, permut = 1000)
print(phylo_D_result)
```

M1 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M1, permut = 1000)
print(phylo_D_result)
```

M2 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M2, permut = 1000)
print(phylo_D_result)
```

Asterales
```{r}
# Specify the tips to keep
tips_to_keep <- c("Achillea_ageratum","Achillea_millefolium","Ageratum_conyzoides","Anaphalis_contorta",      "Arnica_montana","Artemisia_annua","Calendula_officinalis","Carduus_pycnocephalus","Centaurea_armena",        "Centaurea_depressa","Centratherum_punctatum","Chamaemelum_nobile","Chrysactinia_mexicana","Chrysanthemum_coronarium",   "Crassocephalum_crepidiodes","Leontopodium_alpinum","Matricaria_chamomilla","Matricara_recutita","Mikania_glomerata",    "Saussurea_costus","Tagetes_minuta","Tanacetum_parthenium")
# Drop the specified tips
tree_asterales <- keep.tip(tree, tips_to_keep)
```

EXT_structural classes
```{r}
selected_orders <- "Asterales"
EXT_str_asterales <- EXT_str %>% filter(Order %in% selected_orders)
unique(EXT_str_asterales$Taxa_Tips)
```

Check if the matrix and tree tips match
```{r}
identical(sort(tree_asterales$tip.label), sort(EXT_str_asterales$Taxa_Tips)) 
```

Calculation of D-stats
```{r}
physig <- comparative.data(tree_asterales, EXT_str_asterales, names.col = "Taxa_Tips", vcv = TRUE, warn.dropped = TRUE)
```

M0 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M0, permut = 1000)
print(phylo_D_result) #Single state
```

M1 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M1, permut = 1000)
print(phylo_D_result) #Single state
```

M2 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M2, permut = 1000)
print(phylo_D_result) 
```

M3 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M3, permut = 1000)
print(phylo_D_result) 
```

M4 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M4, permut = 1000)
print(phylo_D_result) 
```

M5 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M5, permut = 1000)
print(phylo_D_result) 
```

EXT_biosynthetic classes
```{r}
selected_orders <- "Asterales"
EXT_bio_asterales <- EXT_bio %>% filter(Order %in% selected_orders)
```

Check if the matrix and tree tips match
```{r}
identical(sort(tree_asterales$tip.label), sort(EXT_bio_asterales$Taxa_Tips)) 
```

Calculation of D-stats
```{r}
physig <- comparative.data(tree_asterales, EXT_bio_asterales, names.col = "Taxa_Tips", vcv = TRUE, warn.dropped = TRUE)
```

M0 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M0, permut = 1000)
print(phylo_D_result) #Single state
```

M1 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M1, permut = 1000)
print(phylo_D_result) 
```

M2 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M2, permut = 1000)
print(phylo_D_result) 
```

Lamiaceae
```{r}
# Specify the tips to keep
tips_to_keep <- c("Caryopteris_sp","Clinopodium_vulgare","Dracocephalum_moldavica","Elsholtzia_blanda","Elsholtzia_ciliata","Elsholtzia_densa","Elsholtzia_fruticosa","Hyssopus_officinalis","Lavandula_angustifolia","Marrubium_peregrinum","Marrubium_vulgare","Melissa_officinalis","Mentha_arvensis","Mentha_canadensis","Mentha_longifolia","Mentha_spicata","Monarda_citriodora","Monardo_didyma","Nepeta_cataria","Ocimum_americanum","Ocimum_basilicum","Origanum_vulgare","Pogostemon_cablin","Rosamarinus_officinalis","Salvia_fruticosa","Salvia_officinalis",
"Salvia_sclarea","Satureja_hortensis","Stachys_byzantina","Thymus_pulegiodes","Thymus_vulgaris")
# Drop the specified tips
tree_lamiaceae <- keep.tip(tree, tips_to_keep)
```

EXT_structural classes
```{r}
selected_families <- "Lamiaceae"
EXT_str_lamiaceae <- EXT_str %>% filter(Family %in% selected_families)
unique(EXT_str_lamiaceae$Taxa_Tips)
```

Check if the matrix and tree tips match
```{r}
identical(sort(tree_lamiaceae$tip.label), sort(EXT_str_lamiaceae$Taxa_Tips)) #TRUE
```
Calculation of D-stats
```{r}
physig <- comparative.data(tree_lamiaceae, EXT_str_lamiaceae, names.col = "Taxa_Tips", vcv = TRUE, warn.dropped = TRUE)
```

M0 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M0, permut = 1000)
print(phylo_D_result) #Single state
```
M1 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M1, permut = 1000)
print(phylo_D_result) #Single state
```
M2 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M2, permut = 1000)
print(phylo_D_result) 
```
M3 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M3, permut = 1000)
print(phylo_D_result) 
```
M4 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M4, permut = 1000)
print(phylo_D_result) 
```
M5 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M5, permut = 1000)
print(phylo_D_result) 
```

EXT_biosynthetic classes
```{r}
selected_families <- "Lamiaceae"
EXT_bio_lamiaceae <- EXT_bio %>% filter(Family %in% selected_families)
```

Check if the matrix and tree tips match
```{r}
identical(sort(tree_lamiaceae$tip.label), sort(EXT_bio_lamiaceae$Taxa_Tips)) #TRUE
```
Calculation of D-stats
```{r}
physig <- comparative.data(tree_lamiaceae, EXT_bio_lamiaceae, names.col = "Taxa_Tips", vcv = TRUE, warn.dropped = TRUE)
```

M0 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M0, permut = 1000)
print(phylo_D_result) #Single state
```
M1 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M1, permut = 1000)
print(phylo_D_result) 
```
M2 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M2, permut = 1000)
print(phylo_D_result) 
```

Moraceae
```{r}
# Specify the tips to keep
tips_to_keep <- c("Ficus_aurata","Ficus_beccarii","Ficus_benjamina","Ficus_condensa","Ficus_crassiramea","Ficus_deltoidea","Ficus_fulva",
"Ficus_megaleia","Ficus_microcarpa","Ficus_obscura","Ficus_punctata","Ficus_stolonifera")
# Drop the specified tips
tree_moraceae <- keep.tip(tree, tips_to_keep)
```

EXT_structural classes
```{r}
selected_families <- "Moraceae"
EXT_str_moraceae <- EXT_str %>% filter(Family %in% selected_families)
unique(EXT_str_moraceae$Taxa_Tips)
```
Check if the matrix and tree tips match
```{r}
identical(sort(tree_moraceae$tip.label), sort(EXT_str_moraceae$Taxa_Tips)) #TRUE
```
Calculation of D-stats
```{r}
physig <- comparative.data(tree_moraceae, EXT_str_moraceae, names.col = "Taxa_Tips", vcv = TRUE, warn.dropped = TRUE)
```

M0 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M0, permut = 1000)
print(phylo_D_result) 
```

M1 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M1, permut = 1000)
print(phylo_D_result) #Single state
```
M2 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M2, permut = 1000)
print(phylo_D_result) 
```
M3 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M3, permut = 1000)
print(phylo_D_result) 
```
M4 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M4, permut = 1000)
print(phylo_D_result) 
```
M5 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M5, permut = 1000)
print(phylo_D_result) 
```
EXT_biosynthetic classes
```{r}
selected_families <- "Moraceae"
EXT_bio_moraceae <- EXT_bio %>% filter(Family %in% selected_families)
```

Check if the matrix and tree tips match
```{r}
identical(sort(tree_moraceae$tip.label), sort(EXT_bio_moraceae$Taxa_Tips)) #TRUE
```
Calculation of D-stats
```{r}
physig <- comparative.data(tree_moraceae, EXT_bio_moraceae, names.col = "Taxa_Tips", vcv = TRUE, warn.dropped = TRUE)
```

M0 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M0, permut = 1000)
print(phylo_D_result) #Single state
```
M1 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M1, permut = 1000)
print(phylo_D_result) 
```
M2 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M2, permut = 1000)
print(phylo_D_result) 
```

Rosaceae
```{r}
# Specify the tips to keep
tips_to_keep <- c("Malus_domestica","Prunus_armeniaca","Prunus_avium","Prunus_domestica","Prunus_padus","Prunus_persica","Rosa_chinensis",
"Rosa_gallica","Rosa_odorata_gigantea")
# Drop the specified tips
tree_rosaceae <- keep.tip(tree, tips_to_keep)
```

EXT_structural classes
```{r}
selected_families <- "Rosaceae"
EXT_str_rosaceae <- EXT_str %>% filter(Family %in% selected_families)
unique(EXT_str_rosaceae$Taxa_Tips)
```
Check if the matrix and tree tips match
```{r}
identical(sort(tree_rosaceae$tip.label), sort(EXT_str_rosaceae$Taxa_Tips)) #TRUE
```
Calculation of D-stats
```{r}
physig <- comparative.data(tree_rosaceae, EXT_str_rosaceae, names.col = "Taxa_Tips", vcv = TRUE, warn.dropped = TRUE)
```
M0 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M0, permut = 1000)
print(phylo_D_result) 
```
M1 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M1, permut = 1000)
print(phylo_D_result) #Single state
```
M2 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M2, permut = 1000)
print(phylo_D_result) 
```
M3 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M3, permut = 1000)
print(phylo_D_result) 
```
M4 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M4, permut = 1000)
print(phylo_D_result) 
```
M5 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M5, permut = 1000)
print(phylo_D_result) 
```

EXT_biosynthetic classes
```{r}
selected_families <- "Rosaceae"
EXT_bio_rosaceae <- EXT_bio %>% filter(Family %in% selected_families)
```

Check if the matrix and tree tips match
```{r}
identical(sort(tree_rosaceae$tip.label), sort(EXT_bio_rosaceae$Taxa_Tips)) #TRUE
```
Calculation of D-stats
```{r}
physig <- comparative.data(tree_rosaceae, EXT_bio_rosaceae, names.col = "Taxa_Tips", vcv = TRUE, warn.dropped = TRUE)
```

M0 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M0, permut = 1000)
print(phylo_D_result) 
```
M1 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M1, permut = 1000)
print(phylo_D_result) 
```
M2 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M2, permut = 1000)
print(phylo_D_result) 
```

Myrtaceae
```{r}
# Specify the tips to keep
tips_to_keep <- c("Backhousia_citriodora","Callistemon_citrinus","Callistemon_viminalis","Corymbia_citriodora","Eucalyptus_alba",
"Eucalyptus_camaldulensis","Eucalyptus_deglupta","Eucalyptus_globulus","Eucalyptus_propinqua","Eucalyptus_robusta","Eucalyptus_saligna",
"Eucalyptus_tereticornis","Eucalyptus_urophylla","Eugenia_uniflora","Melaleuca_sp","Myrtus_communis")
# Drop the specified tips
tree_myrtaceae <- keep.tip(tree, tips_to_keep)
```

EXT_structural classes
```{r}
selected_families <- "Myrtaceae"
EXT_str_myrtaceae <- EXT_str %>% filter(Family %in% selected_families)
unique(EXT_str_myrtaceae$Taxa_Tips)
```
Check if the matrix and tree tips match
```{r}
identical(sort(tree_myrtaceae$tip.label), sort(EXT_str_myrtaceae$Taxa_Tips)) #TRUE
```
Calculation of D-stats
```{r}
physig <- comparative.data(tree_myrtaceae, EXT_str_myrtaceae, names.col = "Taxa_Tips", vcv = TRUE, warn.dropped = TRUE)
```

M0 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M0, permut = 1000)
print(phylo_D_result) #Single state
```
M1 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M1, permut = 1000)
print(phylo_D_result) #Single state
```
M2 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M2, permut = 1000)
print(phylo_D_result) 
```
M3 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M3, permut = 1000)
print(phylo_D_result) 
```
M4 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M4, permut = 1000)
print(phylo_D_result) 
```
M5 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M5, permut = 1000)
print(phylo_D_result) 
```

EXT_biosynthetic classes
```{r}
selected_families <- "Myrtaceae"
EXT_bio_myrtaceae <- EXT_bio %>% filter(Family %in% selected_families)
```

Check if the matrix and tree tips match
```{r}
identical(sort(tree_myrtaceae$tip.label), sort(EXT_bio_myrtaceae$Taxa_Tips)) #TRUE
```
Calculation of D-stats
```{r}
physig <- comparative.data(tree_myrtaceae, EXT_bio_myrtaceae, names.col = "Taxa_Tips", vcv = TRUE, warn.dropped = TRUE)
```

M0 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M0, permut = 1000)
print(phylo_D_result) #Single state
```
M1 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M1, permut = 1000)
print(phylo_D_result) 
```
M2 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M2, permut = 1000)
print(phylo_D_result) 
```

Apiaceae
```{r}
# Specify the tips to keep
tips_to_keep <- c("Anethuum_graveolens","Angelica_sylvestris","Anthriscus_cerefolium","Apium_graveolens","Carum_carvi","Centella_asiatica",
"Conopodium_majus","Coriandrum_sativum","Crithmum_maritimum","Cuminum_cyminum","Foeniculum_vulgare","Levisticum_officinale",
"Meum_athamanticum","Oenanthe_crocata","Oliveria_decumbens","Petroselinum_crispum","Pimpinella_saxifraga")
# Drop the specified tips
tree_apiaceae <- keep.tip(tree, tips_to_keep)
```

EXT_structural classes
```{r}
selected_families <- "Apiaceae"
EXT_str_apiaceae <- EXT_str %>% filter(Family %in% selected_families)
unique(EXT_str_apiaceae$Taxa_Tips)
```
Check if the matrix and tree tips match
```{r}
identical(sort(tree_apiaceae$tip.label), sort(EXT_str_apiaceae$Taxa_Tips)) #TRUE
```
Calculation of D-stats
```{r}
physig <- comparative.data(tree_apiaceae, EXT_str_apiaceae, names.col = "Taxa_Tips", vcv = TRUE, warn.dropped = TRUE)
```
M0 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M0, permut = 1000)
print(phylo_D_result) #Single state
```
M1 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M1, permut = 1000)
print(phylo_D_result) 
```
M2 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M2, permut = 1000)
print(phylo_D_result) 
```
M3 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M3, permut = 1000)
print(phylo_D_result) 
```
M4 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M4, permut = 1000)
print(phylo_D_result) 
```
M5 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M5, permut = 1000)
print(phylo_D_result) 
```

EXT_biosynthetic classes
```{r}
selected_families <- "Apiaceae"
EXT_bio_apiaceae <- EXT_bio %>% filter(Family %in% selected_families)
```

Check if the matrix and tree tips match
```{r}
identical(sort(tree_apiaceae$tip.label), sort(EXT_bio_apiaceae$Taxa_Tips)) #TRUE
```
Calculation of D-stats
```{r}
physig <- comparative.data(tree_apiaceae, EXT_bio_apiaceae, names.col = "Taxa_Tips", vcv = TRUE, warn.dropped = TRUE)
```

M0 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M0, permut = 1000)
print(phylo_D_result) #Single state
```
M1 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M1, permut = 1000)
print(phylo_D_result) 
```
M2 mapping
```{r}
set.seed(1234)
phylo_D_result <- phylo.d(physig, binvar = M2, permut = 1000)
print(phylo_D_result) 
```


Run adjusted p-values within each clade
```{r}
#Whole tree
p_random <- c(0.018,0,0,0,0,0.038,0.008,0,0.084)
p_brownian <- c(0,0,0,0.001,0,0,0.023,0,0)

results_wholeTree<- data.frame(
  p_random = p_random,
  p_brownian = p_brownian
)


results_wholeTree$p_random_fdr <- p.adjust(
 results_wholeTree$p_random,
  method = "BH"
)

results_wholeTree$p_brownian_FDR <- p.adjust(
  results_wholeTree$p_brownian,
  method = "BH"
)
```

```{r}
#Rosids
p_random <- c(0.371,0,0.013,0,0.003,0.457,0.301,0.013,0.019)
p_brownian <- c(0.018,0.005,0.191,0.033,0.004,0.002,0.116,0.191,0.072)

results_rosids<- data.frame(
  p_random = p_random,
  p_brownian = p_brownian
)


results_rosids$p_random_fdr <- p.adjust(
 results_rosids$p_random,
  method = "BH"
)

results_rosids$p_brownian_FDR <- p.adjust(
  results_rosids$p_brownian,
  method = "BH"
)
```

```{r}
#Asterids
p_random <- c(0.105,0.003,0.513,0,0.027,0.365,0.215,0.513,0.468)
p_brownian <- c(0.163,0.005,0.003,0.326,0,0.034,0.388,0.003,0.019)

results_asterids<- data.frame(
  p_random = p_random,
  p_brownian = p_brownian
)


results_asterids$p_random_fdr <- p.adjust(
results_asterids$p_random,
  method = "BH"
)

results_asterids$p_brownian_FDR <- p.adjust(
  results_asterids$p_brownian,
  method = "BH"
)
```

```{r}
#Malvids
p_random <- c(0.076,0.284,0.389,0.029,0.68,0.6,0.02,0.389,0.463)
p_brownian <- c(0.623,0.009,0.247,0.37,0.001,0.115,0.918,0.247,0.366)

results_malvids<- data.frame(
  p_random = p_random,
  p_brownian = p_brownian
)


results_malvids$p_random_fdr <- p.adjust(
results_malvids$p_random,
  method = "BH"
)

results_malvids$p_brownian_FDR <- p.adjust(
  results_malvids$p_brownian,
  method = "BH"
)
```


```{r}
#Fabids
p_random <- c(0.691,0,0.011,0.006,0.024,0.495,0.774,0.011,0.081)
p_brownian <- c(0.019,0.123,0.373,0.041,0.014,0.001,0.032,0.373,0.033)

results_fabids<- data.frame(
  p_random = p_random,
  p_brownian = p_brownian
)


results_fabids$p_random_fdr <- p.adjust(
results_fabids$p_random,
  method = "BH"
)

results_fabids$p_brownian_FDR <- p.adjust(
 results_fabids$p_brownian,
  method = "BH"
)
```


```{r}
#Lamids
p_random <- c(0.08,0.011,0.292,0.001,0.177,0.416,0.22,0.292,0.745)
p_brownian <- c(0.37,0.083,0.082,0.387,0.011,0.093,0.274,0.082,0.157)

results_lamids<- data.frame(
  p_random = p_random,
  p_brownian = p_brownian
)


results_lamids$p_random_fdr <- p.adjust(
results_lamids$p_random,
  method = "BH"
)

results_lamids$p_brownian_FDR <- p.adjust(
results_lamids$p_brownian,
  method = "BH"
)
```

```{r}
#Commelinids
p_random <- c(0.382,0.128,0.748,0.139,0.322,0.128,0.318)
p_brownian <- c(0.001,0.1,0.056,0.019,0.066,0.1,0.221)

results_commelinids<- data.frame(
  p_random = p_random,
  p_brownian = p_brownian
)


results_commelinids$p_random_fdr <- p.adjust(
results_commelinids$p_random,
  method = "BH"
)

results_commelinids$p_brownian_FDR <- p.adjust(
results_commelinids$p_brownian,
  method = "BH"
)
```

```{r}
#Magnoliids
p_random <- c(0.205,0.365,0.113,0.114,0.887,0.007,0.205,0.113,0.414)
p_brownian <- c(0.172,0.006,0.018,0.048,0,0.485,0.172,0.018,0.091)

results_magnoliids<- data.frame(
  p_random = p_random,
  p_brownian = p_brownian
)


results_magnoliids$p_random_fdr <- p.adjust(
results_magnoliids$p_random,
  method = "BH"
)

results_magnoliids$p_brownian_FDR <- p.adjust(
results_magnoliids$p_brownian,
  method = "BH"
)
```

```{r}
#Myrtales
p_random <- c(0.112,0.263,0.421,0.014,0.149,0.259,0.421)
p_brownian <- c(0.629,0.092,0.202,0.624,0.378,0.499,0.202)

results_myrtales<- data.frame(
  p_random = p_random,
  p_brownian = p_brownian
)


results_myrtales$p_random_fdr <- p.adjust(
results_myrtales$p_random,
  method = "BH"
)

results_myrtales$p_brownian_FDR <- p.adjust(
results_myrtales$p_brownian,
  method = "BH"
)
```

```{r}
#Rosales
p_random <- c(0.562,0.074,0.013,0.192,0.745,0.358,0.543,0.013,0.334)
p_brownian <- c(0.095,0.168,0.627,0.069,0.005,0.08,0.233,0.627,0.041)

results_rosales<- data.frame(
  p_random = p_random,
  p_brownian = p_brownian
)


results_rosales$p_random_fdr <- p.adjust(
results_rosales$p_random,
  method = "BH"
)

results_rosales$p_brownian_FDR <- p.adjust(
results_rosales$p_brownian,
  method = "BH"
)
```

```{r}
#Lamiales
p_random <- c(0.031,0.035,0.371,0.02,0.083,0.45,0.126,0.371,0.633)
p_brownian <- c(0.689,0.185,0.063,0.527,0.109,0.095,0.566,0.063,0.221)

results_lamiales<- data.frame(
  p_random = p_random,
  p_brownian = p_brownian
)


results_lamiales$p_random_fdr <- p.adjust(
results_lamiales$p_random,
  method = "BH"
)

results_lamiales$p_brownian_FDR <- p.adjust(
results_lamiales$p_brownian,
  method = "BH"
)
```

```{r}
#Asteraceae
p_random <- c(0.48,0.886,0.346,0.355,0.886,0.905)
p_brownian <- c(0.285,0.009,0.122,0.386,0.009,0)

results_asteraceae<- data.frame(
  p_random = p_random,
  p_brownian = p_brownian
)


results_asteraceae$p_random_fdr <- p.adjust(
results_asteraceae$p_random,
  method = "BH"
)

results_asteraceae$p_brownian_FDR <- p.adjust(
results_asteraceae$p_brownian,
  method = "BH"
)
```

```{r}
#Lamiaceae
p_random <- c(0.013,0.148,0.271,0.015,0.687,0.148)
p_brownian <- c(0.552,0.282,0.589,0.511,0.162,0.282)

results_lamiaceae<- data.frame(
  p_random = p_random,
  p_brownian = p_brownian
)


results_lamiaceae$p_random_fdr <- p.adjust(
results_lamiaceae$p_random,
  method = "BH"
)

results_lamiaceae$p_brownian_FDR <- p.adjust(
results_lamiaceae$p_brownian,
  method = "BH"
)
```

```{r}
#Moraceae
p_random <- c(0.171,0,0,0.557,0.722,0.955,0,0.711)
p_brownian <- c(0.499,1,0.957,0.078,0.055,0,0.957,0.042)

results_moraceae<- data.frame(
  p_random = p_random,
  p_brownian = p_brownian
)


results_moraceae$p_random_fdr <- p.adjust(
results_moraceae$p_random,
  method = "BH"
)

results_moraceae$p_brownian_FDR <- p.adjust(
results_moraceae$p_brownian,
  method = "BH"
)
```

```{r}
#Rosaceae
p_random <- c(0.517,0.553,0.543,0.02,0.496,0.02,0.517,0.543,0.02)
p_brownian <- c(0.191,0.101,0.191,0.855,0.162,0.855,0.191,0.191,0.855)

results_rosaceae<- data.frame(
  p_random = p_random,
  p_brownian = p_brownian
)


results_rosaceae$p_random_fdr <- p.adjust(
results_rosaceae$p_random,
  method = "BH"
)

results_rosaceae$p_brownian_FDR <- p.adjust(
results_rosaceae$p_brownian,
  method = "BH"
)
```

```{r}
#Myrtaceae
p_random <- c(0.164,0.345,0.067,0.218,0.15,0.354)
p_brownian <- c(0.231,0.233,0.71,0.394,0.588,0.233)

results_myrtaceae<- data.frame(
  p_random = p_random,
  p_brownian = p_brownian
)


results_myrtaceae$p_random_fdr <- p.adjust(
results_myrtaceae$p_random,
  method = "BH"
)

results_myrtaceae$p_brownian_FDR <- p.adjust(
results_myrtaceae$p_brownian,
  method = "BH"
)
```

```{r}
#Apiaceae
p_random <- c(0.767,0.455,0.185,0.185,0.034,0.185,0.395)
p_brownian <- c(0.095,0.117,0.71,0.71,0.669,0.71,0.332)

results_apiaceae<- data.frame(
  p_random = p_random,
  p_brownian = p_brownian
)


results_apiaceae$p_random_fdr <- p.adjust(
results_apiaceae$p_random,
  method = "BH"
)

results_apiaceae$p_brownian_FDR <- p.adjust(
results_apiaceae$p_brownian,
  method = "BH"
)
```
